\documentclass[]{deedy-resume-openfont}


\begin{document}

\namesection{Maksim}{Charchuk}{maxim.cherchuk@gmail.com | +37529-110-1128}


\begin{minipage}[t]{0.40\textwidth}

\section{Education} 
\large
\subsection{Belarusian State University}
\descript{Faculty of Applied Mathematics and computer science}
\descript{Bachelor in Computer Science}
\location{Grad. June 2018 | Minsk, Belarus}
\sectionsep
\sectionsep

\subsection{Lyceum of BSU}
\descript{Grad. June 2014 | Minsk, Belarus}



\end{minipage} 
\hfill
\begin{minipage}[t]{0.59\textwidth} 


\section{Coursework}
\large
Data Structures and Algorithms \\
3D Graphics \\
Computer Vision \\
Expressions Parsing \\
\sectionsep

\end{minipage} 

\vspace{\topsep}

\begin{minipage}[t]{0.40\textwidth}

\section{Links}
\large
Github://\href{https://github.com/MaximCherchuk}{\custombold{MaximCherchuk}} \\
LinkedIn://\href{https://www.linkedin.com/in/maxim-cherchuk-6305aaa5/}{\custombold{maxim-cherchuk}} \\
Codeforces://\href{http://codeforces.com/profile/MaxCherchuk}{\custombold{MaximCherchuk}} \\
Facebook://\href{https://www.facebook.com/profile.php?id=100004263036771}{\custombold{Maxim Cherchuk}}
\sectionsep

\end{minipage}
\begin{minipage}[t]{0.59\textwidth}

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
\large
Java \textbullet{} Python \textbullet{} C++\ \\
\sectionsep
\location{Over 1000 lines:}
\large
C \textbullet{} C\# \textbullet{} \LaTeX \\
\sectionsep

\location{Strong skills:}
\large
SQL \textbullet{} PostgreSQL \textbullet{} Bash
\sectionsep

\location{Familiar:}
\large
\textbullet{} OrientDB \textbullet{} JavaScript \textbullet{} PyOpenCV
\sectionsep

\subsection{Languages}
\vspace{\topsep}
\begin{tightemize}
\item Russian: Native
\item English: Advanced (speaking, reading, writing)
\end{tightemize}
\sectionsep
\end{minipage}

\section{WORK EXPERIENCE}

\section{{\custombold{Invento Labs}}}

\descript{C++/Python Developer}
\location{February 2017 – October 2017 | Minsk, Belarus}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\large
\item Worked on 3D Blender renderer needed to apply materials selected for the model and demonstrate 3D models in real time.
\item Implemented Django backend for the rendering system.
\item All code was reviewed, perfected, and pushed to production.
\end{tightemize}
\sectionsep


\section{{\custombold{iTechArt Group}}}

\descript{Python Developer}
\location{March 2018 – present | Minsk, Belarus}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\large
\item Work on \href{https://smiledirectclub.com}{{\custombold{smiledirectclub.com}}} backend.
\item Implement microservices and payment systems.
\item Integrate the microservices with AWS.
\end{tightemize}
\sectionsep


\vspace{\topsep}
\begin{minipage}[t]{1\textwidth}
\section{Technical Experience}
\begin{tightemize}
\vspace{\topsep}
\large
\item Implemented a lot of fancy features for Minetest. C++
\item Working on CV system calculating paths and managing objects in real time. Python
\item Developed a 3D Java Engine for showing different 3D-model types. Java


\end{tightemize}
\sectionsep
\end{minipage}

\end{document}
