%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {EPAM Systems} % Organization
    {Minsk, Belarus} % Location
    {Aug. 2021 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Work on the \href{https://www.enverus.com/}{Enverus} internal document processing system.}
        \item {Implemented directional survey calculations.}
        \item {Participated in decision-making and architect meeting.}
        \item {Worked on project infrastructure and scaling.}
        \item {Implemented RESTful API for the data services.}
        \item {Worked on data design and data migration.}
        \item {Covered the backend with unit/integration tests.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {EPAM Systems} % Organization
    {Minsk, Belarus} % Location
    {Nov. 2019 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the new \href{www.hulu.com}{Hulu} financial system.}
        \item {Optimized and improved legacy financial system database.}
        \item {Led a small team of developers.}
        \item {Implemented RESTful API for the new financial system.}
        \item {Implemented calculation logic in SQL and integrated it with the API.}
        \item {Covered the backend with unit/integration tests.}
        \item {Worked on data migration from the legacy to the new database.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Softensity} % Organization
    {Minsk, Belarus} % Location
    {Mar. 2018 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on \href{www.smiledirectclub.com}{smiledirectclub.com} backend and microservices.}
        \item {Implemented microservices for the authentication and payment systems in Python/Tornado.}
        \item {Implemented RESTful API for the authentication utilizing Docker and AWS Cognito.}
        \item {Implemented several API microservices and the serverless AWS Lambda functions.}
        \item {Integrated the microservices with AWS stack (Including ECS, ECR, S3, CloudFront, RDS, IAM).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Invento Labs} % Organization
    {Minsk, Belarus} % Location
    {Feb. 2017 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a Blender rendering system creating 3D models of clothes and saving the models in .mesh/.html5 formats.}
        \item {Implemented Django backend for the rendering system.}
        \item {Implemented RESTful API server for the rendering system.}
        \item {Built and deployed overall service infrastructure and CI/CD utilizing Docker containers, Jenkins and Postgres, focusing on fault tolerance.}
        \item {All code was reviewed, perfected, and pushed to production.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
